Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
overall edits

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    %\midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. \Fix{Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.}\Mar{did not
  review part in red}

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines. More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines.

@@

@@

\Fix{We mined JS programs from the GitHub repository. In this case, we searched
for projects written in JavaScript, that were tagged with ``javascript-engine",
and that have both ``Javascript" and ``engine" the name or the description of
the project. After this process, we ended up with 2200 JS programs, which we
downloaded locally. However, after careful investigation, we noted that 160 of
these projects do not  have any JS file, which were excluded from our study.
We used the 2040 remaining ones as input to our testing approaches.}

@@

\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc code base.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.}
At the bottom of this figure, there is a sequence of
three elements that we use to characterize a warning--1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs (when compared with,
for instance, AFL).

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.
\Fix{For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios.
We performed seven consecutive executions because,
since the studied JS engines release new versions on a daily basis,
we wanted to make sure if the failing tests raised by the Test262 suite
were rapidly fixed by the maintenance team. If these errors were quickly
fixed, that would suggest that this given engine would be aligned with
the ECMAScript specification.}
Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}.

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
worse when compared to the other engines.
\Fix{This happens because \hermes
still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \chakra\ also a low passing ratio
in this test suite and the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As aforementioned,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \textbf{\chakra}.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \textbf{\chakra} development team as a
bug, but they did \emph{not} accept.

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case original from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represents octal
numeric literals. It was an issue which explores a deprecated octal
token after ASI (Automatic Semicolon Insertion).  The others engine
throws a SyntaxError due the missing of the octal token, but \smonkey
returns a integer 8 that represents 010 in octal.

%% \begin{figure}[h!]
%%   \vspace{-0.5ex}
%%   \centering
%%   \scriptsize
%%   \lstset{escapeinside={@}{@},
%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%%     numberstyle=\tiny,
%%     morekeywords={assertEq, var, yield, in, function,
%%     typeof, return, throw, new, Error, if},
%%   }
%%   \begin{lstlisting}
%%     "use strict"
%%     010
%%   \end{lstlisting}
%%   \normalsize
%%   %% \caption{Warning captured as \hi{} priority.}
%%   %% \label{fig:hi-priority}
%%   \vspace{-1ex}
%% \end{figure}

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation. 
This is a case of validation of RegExp flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
but this flag is not valid. The behavior expected is throws an early
SyntaxError due to a invalid regular expression flag,
but \hermes\ seems not treats the early validation of the regexp flags
as commented by a maintainer.

@@

\subsection{Key Findings}
\label{sec:findings}

@@

\begin{enumerate}
  \item Both techniques we studied have shown to be practical and
    effective to find bugs on real, complex, and widely used software
    systems;
  \item Even for language APIs with fairly clear specs, as it is the
    case of JavaScript, there is likely (a lot of) variation between
    different implementations, which brings intrinsic challenges to
    developers that work on them;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;

\end{enumerate}

%% 3)~Not only multiple different
%% implementations can be leveraged in differential testing, but
%% differences in test suites can also be important.

The main findings of this study are as follows: 1) The techniques we
selected found, with relatively low effort, several bugs even in very
robust engines, such as Mozilla's \smonkey, 2)~Even for software
projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
implementation-specific behaviors whose implementation can
inadvertedly lead to interference in the well-specified parts of the
spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
differential testing is feasible on real, complex, widely used pieces
of software. Even black-box mutational fuzzers revealed bugs. We do
expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
black-box grammar-based generational fuzzers) could reveal even more
bugs

\subsection{Key Lessons}
\label{sec:lessons}

The key lessons of this study are as follows:

\begin{enumerate}
\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
  should be encouraged;
\item The cost of inspection of the warnings in differential testing
  should be reduced;
\item Finding bugs in large software is a very effective way to engage
  student in contributing to open-source software and learning
  Software Testing practices.
\end{enumerate}

1)~When taking into consideration our bug finding campaign, Mozilla's
\smonkey\ and Google's \veight\ stood out as the most reliable
engines. Therefore, we recommend the use of these engine for running
\js\ applications. 2)~Further reducing cost of inspection in
differential testing is an important problem. Although the inspection
activity was not uninterrupted, it is safe to say that each warning
required a substantial amount of time to analyze for potential false
alarms. In fact, many \hi\ warnings reported with differential testing
were not analyzed. We observed empirically that the cost of analysis
was proportional to (i) the \js\ specification covered by the original
test (as developers need to read and understand those parts) and (ii)
the availability of alternative implementations. We prefer to see such
problem as an opportunity for future research. For example, applying
learning techniques to prioritize the warnings more likely to be
faulty (in the spirit of the work of Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
avenue to explore. Recall that the rate of true positives of the
techniques we studied is rather small. 3)~We learned that reporting
real bugs is a great way to train (and encourage) students in software
testing. Students praised the experience of diagnosing failures,
understanding part of the specs (as needed), writing bug reports,
participating in discussions on issue trackers, and observing the
change of status. That was a relatively self-contained hands-on
activity that enabled students to engage in a real-life serious
industrial project.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
% LocalWords:  PRONEX
<

>>>>

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, as aforementioned,
we did not consider tests from the \chakra{} repository because they depend on
non-portable objects.
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines.

More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to
make the test file work in the other engine.
For instance, if a test had a statement such as \texttt{print(1==1);}
we manually refactored that statement to \texttt{assertEquals(1,1)}.
If the change would require more substantial manual work, we opted to
discard the test instead. Overall we may have manually refactored more
than a thousand test files.

@@

To enrich our dataset of test files, we mined additional tests available on
JavaScript GitHub projects as well as in the issue trackers of the studied
JS engines. We explain this process next.

@@

We mined JS programs from the GitHub repository. In this case, we searched
for projects written in JavaScript, that were tagged with ``javascript-engine",
and that have both ``Javascript" and ``engine" the name or the description of
the project. After this process, we ended up with 2,200 JS programs, which we
downloaded locally. However, after careful investigation, we noted that 160 of
these projects do not have any JS file, which were excluded from our study.
From these 2,040 projects, we could select 494,394 test files,
which we as input to our testing approaches.

@@

Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc code base.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.
At the bottom of this figure, there is a sequence of
three elements that we use to characterize a warning: 1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

We used two black-box mutational fuzzers in this
study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs (when compared with,
for instance, AFL).

@@

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.
For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios.
We performed seven consecutive executions because,
since the studied JS engines release new versions on a daily basis,
we wanted to make sure if the failing tests raised by the Test262 suite
were rapidly fixed by the maintenance team. If these errors were quickly
fixed, this would suggest that this given engine would be closely aligned with
the ECMAScript specification.
Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all engines but \chakra used some
variant of the Test262 suite as part of their regression process.
We used the same version in this
experiment~\cite{ecma262-conformance-suite}.

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight, and \smonkey
%, whereas \chakra performs
%worse when compared to the other engines.
%\Fix{This happens because \hermes
%still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \chakra has a low passing ratio
in this test suite. Intestingly, it is also the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As aforementioned,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \chakra.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \veight{} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\Mar{--------------- estou aqui}

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \jsc.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \chakra\ development team as a
bug, but they did \emph{not} accept.

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \smonkey\ development team as a
bug, the bug was confirmed in a few hours.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    "use strict"
    010
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
  \vspace{-1ex}
\end{figure}

This is a test case original from the \hermes suite using test transplantation.
According the specification, in strict mode, the engine must use
the prefix '0o' or '0O' to represents octal numeric literals. It was an
issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
The others engine throws a SyntaxError due the missing of the octal token, but
\smonkey returns a integer 8 that represents 010 in octal literal.

@@

\subsection{Key Findings and Lessons}
\label{sec:lessons}

@@

\begin{itemize}
  \item Both techniques we investigated were successful in revealing
    bugs (several of them);
  %% \item We have found more bugs with test transplantation than we have
  %%   with cross-engine differential testing. In addition, test
  %%   transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs. We conjecture that there is room to find more
    bugs using other fuzzers;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we analyzed, with Google's \veight\ after it.
\end{itemize}

The main lessons we learned from this study are as follows: 1)~Even
for software projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
variation between different implementations and, therefore,
opportunities for bugs. 2)~Not only multiple different implementations
can be leveraged in differential testing, but differences in test
suites can also be important. 3)~Finding functional/non-crash bugs
with differential testing is feasible on real, complex, widely used
pieces of software. 4)~Further reducing cost of inspection is an
important problem. Although the inspection activity was not
uninterrupted, it is safe to say that each warning required a
substantial amount of time to analyze for potential false alarms. In
fact, many \hi\ warnings reported with differential testing were not
analyzed. In determining cost, we observed, from experience, that the
complexity of the \js\ specifications that the original test covers
increases cost of diagnosing (as developers need to read and
understand those) and the availability of alternative implementations
(for the cases warnings are revealed through differential testing)
reduces the cost of diagnosis. We prefer to see such problem as an
opportunity for future research. For example, applying learning
techniques to prioritize the warnings more likely to be faulty (in the
spirit of the work of Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
avenue to explore. Recall that the rate of true positives of the
techniques we studied is rather small.  5)~We learned that reporting
real bugs is a great way to train (and encourage) students in software
testing. Students praised the experience of diagnosing failures,
understanding part of the specs (as needed), writing bug reports,
participating in discussions on issue trackers, and observing the
change of status. That was a relatively self-contained hands-on
activity that enabled students to engage in a real-life serious
industrial project.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
% LocalWords:  PRONEX
